---
title: "Getting Started"
author: "<h4>Author: <i>Brian M. Schilder</i></h4>"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{Getting Started}
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```


```R
library(`r pkg`)
```

```{r, echo=FALSE}
## Many examples require network access (GitHub API).
## Skip evaluated chunks when offline to keep R CMD check happy.
has_internet <- function() {
    z <- try(suppressWarnings(
        readLines("https://github.com", n = 1L, warn = FALSE)
    ), silent = TRUE)
    !inherits(z, "try-error")
}
run_online <- has_internet()
```

# Gather package metadata

## echoverse

`package_metadata` pulls metadata from the DESCRIPTION files from a package
(or list of packages) and organises them into a convenient table.

Metadata for the [*echoverse*](https://github.com/topics/echoverse) suite of
R packages will be retrieved by default.
While *echoverse* itself is not the name of an R package, `package_metadata`
will automatically recognise this special command and retrieve
all packages that are part of this suite.

```{r metadata1, eval=run_online}
meta_echoverse <- echodeps::package_metadata(pkgs = "echoverse")

knitr::kable(meta_echoverse)
```

## dplyr

You can use the same function to retrieve metadata for any CRAN or
Bioconductor package.

```{r metadata2, eval=run_online}
meta <- echodeps::package_metadata(pkgs = c("dplyr","data.table","igraph"))

knitr::kable(meta)
```


# Create a dependency graph

`dep_graph` builds upon the above functions and creates a dependency graph for
all the dependencies of a given R package
(or a selected subset of its dependencies).

Metadata for each package is automatically extracted and shown as tooltips that
appear when you hover over the respective node.

All of the plots, graphs, metadata, and saved file paths generated by
`dep_graph` are returned to the user as a named list in case they would like
to explore them further.

## echolocatoR

```{r graph1, eval=FALSE}
res_echoverse <- echodeps::dep_graph(pkg = "echolocatoR",
                                     ## Setting show_plot for vignette purposes
                                     show_plot = list(r=TRUE,
                                                      browser=FALSE))
```

## dplyr

```{r graph2, eval=FALSE}
res <- echodeps::dep_graph(pkg = "dplyr",
                           shape = "hexagon",
                           layout = function(graph, pkg){
                               visNetwork::visIgraphLayout(
                                   graph = graph,
                                   layout = "layout_nicely"
                               )
                           }
                           )
```

<hr>

# Session Info

<details>

```{r Session Info}
utils::sessionInfo()
```

</details>

<br>
