---
title: "My packages"
author: "<h4>Author: <i>Brian M. Schilder</i></h4>"
date: "<h4>Updated: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document
vignette: >
    %\VignetteIndexEntry{My packages}
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown}
---


```{r, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
library(pkg, character.only = TRUE)
```


```R
library(`r pkg`)
```

This vignette shows how to use `echodeps` to visualise reverse
dependencies of one of your own packages. The examples below use
`rworkflows` as the seed package and then filter the resulting graph
to packages published by specific GitHub organisations.

# Create graph

```{r, eval=FALSE}
res <- dep_graph(pkg = "rworkflows",
                 method_seed = "github",
                 reverse = TRUE)
```

# Subset graph

Once you have the full reverse-dependency graph you can subset it to
only the packages you maintain. Here we keep nodes whose names
contain known GitHub organisation prefixes.

```{r, eval=FALSE}
mypkgs <- grep("neurogenomics/|bschilder/|RajLabMSSM/|NathanSkene/",
               names(igraph::V(res$graph)),
               value = TRUE)
g <- res$graph |>
    tidygraph::filter(name %in% mypkgs) |>
    dplyr::mutate(size = 60)
```

# Plot network

```{r, eval=FALSE}
plt <- echodeps::dep_graph_plot(g = g,
                                pkg = "rworkflows",
                                use_basename = TRUE)
```


# Session Info

<details>

```{r Session Info}
utils::sessionInfo()
```

</details>

<br>
